Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-22 paper.qmd
Updated gen_axes function

gen_axes <- function(data, proj_data, limits = 1, axis_pos_x = NULL, axis_pos_y = NULL) {

@@

  adj <- function(x, axis_pos) axis_pos + x * axis_scale
  axes <- data.frame(x1 = adj(0, axis_pos_x), 
                     y1 = adj(0, axis_pos_y), 
                     x2 = adj(projection[, 1], axis_pos_x), 
                     y2 = adj(projection[, 2], axis_pos_y))

@@

axes_obj <- gen_axes(
  data = scaled_gau_data,
  proj_data = projected_df,
  limits = 0.2,
  axis_pos_x = 0.15,
  axis_pos_y = -0.85)

@@

axes_obj <- gen_axes(
  data = scaled_gau_data,
  proj_data = projected_df,
  limits = 0.3,
  axis_pos_x = -0.7,
  axis_pos_y = -0.7)

@@

axes_obj <- gen_axes(
  data = scaled_gau_data,
  proj_data = projected_df,
  limits = 0.2,
  axis_pos_x = -0.55,
  axis_pos_y = -0.05)

@@

axes_obj <- gen_axes(
  data = scaled_gau_data,
  proj_data = projected_df,
  limits = 0.2,
  axis_pos_x = -0.37,
  axis_pos_y = 0.22)

@@

axes_obj <- gen_axes(
  data = scaled_pbmc_data, 
  proj_data = projected_df,  
  limits = 1.5,
  axis_pos_x = -0.75,
  axis_pos_y = -0.75)

@@

axes_obj <- gen_axes(
  data = scaled_mnist_data, 
  proj_data = projected_df, 
  limits = 1.5,
  axis_pos_x = -0.75,
  axis_pos_y = -0.75)

>>>>

gen_axes <- function(data, proj_data, proj, limits = 1, axis_pos_x = NULL, axis_pos_y = NULL) {

@@

  adj <- function(x, axis_pos) axis_pos + x * axis_scale
  axes <- data.frame(x1 = adj(0, axis_pos_x), 
                     y1 = adj(0, axis_pos_y), 
                     x2 = adj(proj[, 1], axis_pos_x), 
                     y2 = adj(proj[, 2], axis_pos_y))

@@

axes_obj <- gen_axes(
  data = scaled_gau_data,
  proj_data = projected_df,
  proj = projection,
  limits = 0.2,
  axis_pos_x = 0.15,
  axis_pos_y = -0.85)

@@

axes_obj <- gen_axes(
  data = scaled_gau_data,
  proj_data = projected_df,
  proj = projection,
  limits = 0.3,
  axis_pos_x = -0.7,
  axis_pos_y = -0.7)

@@

axes_obj <- gen_axes(
  data = scaled_gau_data,
  proj_data = projected_df,
  proj = projection,
  limits = 0.2,
  axis_pos_x = -0.55,
  axis_pos_y = -0.05)

@@

axes_obj <- gen_axes(
  data = scaled_gau_data,
  proj_data = projected_df,
  proj = projection,
  limits = 0.2,
  axis_pos_x = -0.37,
  axis_pos_y = 0.22)

@@

axes_obj <- gen_axes(
  data = scaled_pbmc_data, 
  proj_data = projected_df, 
  proj = projection,
  limits = 1.5,
  axis_pos_x = -0.75,
  axis_pos_y = -0.75)

@@

axes_obj <- gen_axes(
  data = scaled_mnist_data, 
  proj_data = projected_df, 
  proj = projection,
  limits = 1.5,
  axis_pos_x = -0.75,
  axis_pos_y = -0.75)
